The \dealii{} Library, Version 8.5

### 2017-03-05 8.5/paper.tex
Improve text

\item Various improvements for high-order elements, including a switch of
  support points in \texttt{FE\_Q} and \texttt{FE\_DGQ} to Gauss--Lobatto
  support points, more stable evaluation of Legendre polynomials, and several
  bugfixes for high-order polynomial mappings defined through the
  \texttt{MappingQ} class.

@@

      x label style={at={(0.5,0.02)}},
      y label style={at={(0.05,0.5)}},

@@

      title={$256^3$ mesh, discontinuous $\mathcal Q_3$ elements},

@@

      x label style={at={(0.5,0.02)}},

@@

High-order Lagrange elements, both continuous \verb!FE_Q! and discontinuous
\verb!FE_DGQ! types, now use the nodal points of the Gauss--Lobatto
quadrature formula as support points, rather than the previous equidistant
ones. For cubic polynomials and higher, the point distribution has changed and
thus the entries in solution vectors will look different now. Note, however,
that using the Gauss--Lobatto points as nodal points results in much more
stable interpolation, including better iteration counts in most iterative
solvers.

>>>>

\item Various improvements for high-order elements, including a switch of
  support points in \texttt{FE\_Q} and \texttt{FE\_DGQ} to Gauss--Lobatto
  support points, stable evaluation of high-order Legendre polynomials, and several
  bugfixes for high-order polynomial mappings defined through the
  \texttt{MappingQ} class.

@@

@@

      title={discontinuous $\mathcal Q_3$ elements},

@@

@@

High-order Lagrange elements, both continuous \verb!FE_Q! and discontinuous
\verb!FE_DGQ! types, now use the nodal points of the Gauss--Lobatto
quadrature formula as support points, rather than the previous equidistant
ones. For cubic polynomials and higher, the point distribution has thus changed and
thus the entries in solution vectors will look different as compared to the previous version. Note, however,
that using the Gauss--Lobatto points as nodal points results in a much more
stable interpolation, including better iteration counts in most iterative
solvers.
